A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-03-15 writeup/paper.tex
equations

% Todo: sort by language code, rebalance the bottom set to have 19 languages in it.
\begin{table}[h]
\scriptsize 
\begin{center}
\begin{tabular}{|p{0.95\linewidth}|}
\hline
{\sc 500k+ articles:}
Dutch (nl), English (en), French (fr), German (de), Italian (it), Japanese (ja), Polish (pl), Portuguese (pt), Russian (ru), Spanish (es)\\
\hline
{\sc 100k-500k articles:} Arabic (ar), Basque (eu), Bulgarian (bg), Catalan (ca), Chinese (zh), Croatian (hr), Czech (cs), Danish (da), Esperanto (eo), Finnish (fi), Hebrew (he), Hindi (hi), Hungarian (hu), Indonesian (id), Kazakh (kk), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Persian (fa), Romanian (ro), Serbian (sr), Slovak (sk), Slovenian (sl), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war)\\
\hline
{\sc 10k-100k articles:}
Azerbaijani (az), Afrikaans (af), Albanian (sq), Amharic (am), Aragonese (an), Armenian (hy), Asturian (ast), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Bosnian (bs), Breton (br), Cebuano (ceb), Galician (gl), Georgian (ka), Greek (el), Gujarati (gu), Haitian (ht), Icelandic (is), Ido (io), Irish (ga), Javanese (jv), Kannada (kn), Kurdish (ku), Latvian (lv), Low Saxon (nds), Luxembourgish (lb), Macedonian (mk), Malagasy (mg), Malayalam (ml), Marathi (mr), Neapolitan (nap), Nepali (ne), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Quechua (qu), Serbo-Croatian (sh), Sicilian (scn), Sundanese (su), Swahili (sw), Tagalog (tl), Tamil (ta), Tatar (tt), Telugu (te), Thai (th), Urdu (ur), Walloon (wa), Welsh (cy), West Frisian (fy), Yoruba (yo), Zazaki (diq)\\
\hline
{\sc $<$10k articles:} Central Bicolano (bcl), Ilokano (ilo), Kapampangan (pam), Pashto (ps), Punjabi (pa), Sindhi (sd), Somali (so), Tibetan (bo), Uzbek (uz), Wolof (wo)\\
\hline
\end{tabular}
\end{center}
\normalsize
\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.  Each language's code is given in parentheses.  These language codes are used in other figures throughout this paper.}\label{wikipedia-buckets}
\end{table}%

@@

In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.  We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows:
\textit{In English, so people know what we did:}
\begin{align}	
	Quality = \frac{\# \text{translations in } Synonyms(\text{answer})}{\# \text{ controls}}
\end{align}	
where answer is the known translation and $Synonyms$(answer) is the set of words judged to be synonymous with the gold standard translation in the second pass HIT.
\textit{Mathified, to give the impression of rigor and intellect:}
\begin{align}	
	Quality = \frac{1}{k}\sum\limits_{i=1}^k\mathbf{1}(t_i \in Synonyms(a_i))
\end{align}	
where $k$ is the number of controls in the assignment, $t_i$ is the Turker's provided translation of control word $i$, $a_i$ is the gold standard translation of the control word $i$, and $Synonyms(a_i)$ is the set of words judged to be synonymous with the $a_i$ in the second pass HIT and $\mathbf{1}(x)$ is 1 when $x$ is true.

Since most assignments had two known words embedded, most assignments had scores of either 0, 0.5, or 1. Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores reported the average per-turker quality in tables and figures, where a Turker's quality is just the average quality of all the assignments that the Turker completed.

>>>>

\begin{table}[h]
\scriptsize 
\begin{center}
\begin{tabular}{|p{0.95\linewidth}|}
\hline
{\sc 500k+ articles:} German (de), English (en), Spanish (es), French (fr), Italian (it), Japanese (ja), Dutch (nl), Polish (pl), Portuguese (pt), Russian (ru)\\
\hline
{\sc 100k-500k articles:} Arabic (ar), Bulgarian (bg), Catalan (ca), Czech (cs), Danish (da), Esperanto (eo), Basque (eu), Persian (fa), Finnish (fi), Hebrew (he), Hindi (hi), Croatian (hr), Hungarian (hu), Indonesian (id), Korean (ko), Lithuanian (lt), Malay (ms), Norwegian (Bokmal) (no), Romanian (ro), Slovak (sk), Slovenian (sl), Serbian (sr), Swedish (sv), Turkish (tr), Ukrainian (uk), Vietnamese (vi), Waray-Waray (war), Chinese (zh)\\
\hline
{\sc 17k-100k articles:}
Afrikaans (af), Azerbaijani (az), Belarusian (be), Bengali (bn), Bishnupriya Manipuri (bpy), Breton (br), Bosnian (bs), Cebuano (ceb), Welsh (cy), Greek (el), West Frisian (fy), Galician (gl), Gujarati (gu), Haitian (ht), Icelandic (is), Javanese (jv), Georgian (ka), Kurdish (ku), Luxembourgish (lb), Latvian (lv), Malagasy (mg), Macedonian (mk), Malayalam (ml), Marathi (mr), Low Saxon (nds), Newar / Nepal Bhasa (new), Norwegian (Nynorsk) (nn), Piedmontese (pms), Sicilian (scn), Serbo-Croatian (sh), Albanian (sq), Swahili (sw), Tamil (ta), Telugu (te), Thai (th), Tagalog (tl), Urdu (ur), Yoruba (yo)\\
\hline
{\sc $<$17k articles:} Amharic (am), Asturian (ast), Central Bicolano (bcl), Tibetan (bo), Zazaki (diq), Irish (ga), Armenian (hy), Ilokano (ilo), Kannada (kn), Neapolitan (nap), Nepali (ne), Punjabi (pa), Kapampangan (pam), Pashto (ps), Sindhi (sd), Somali (so), Sundanese (su), Uzbek (uz), Wolof (wo)\\
\hline
\end{tabular}
\end{center}
\normalsize
\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.  Each language's code is given in parentheses.  These language codes are used in other figures throughout this paper.}\label{wikipedia-buckets}
\end{table}%

@@

In order to address the quality of the translations we received on the dictionary task, we constructed a pipeline in which the output of the translation HIT was reviewed by humans in a second evaluation HIT, described above.  We quantified the quality of each translation assignment based on the output of the evaluation HIT as follows: \\
\textbf{In English, so people know what we did:}
\begin{align}	
	Quality = \frac{\# \text{correct controls}}{\# \text{controls}}
\end{align}	
where a control is correct if it matches or is judged to be synonymous with the gold standard translation during the second pass HIT. \\
\textbf{Mathified, to give the impression of rigor and intellect:}
\begin{align}	
	Quality(assign_i) = \frac{1}{k}\sum\limits_{j=1}^{k_i}\mathbf{1}(t_{ij} \in Syns(a_j))
\end{align}	
where $k_i$ is the number of controls in the assignment $i$, $t_j$ is the Turker's provided translation of control word $j$ in assignment $i$, $a_j$ is the gold standard translation of control word $j$, $Syns(a_j)$ is the set of words judged to be synonymous with $a_j$ during the second pass HIT, and $\mathbf{1}(x)$ is 1 when $x$ is true.

Most assignments had two known words embedded, so most assignments had scores of either 0, 0.5, or 1.

Since by-assignment quality scores are noisy and sensitive to small numbers of highly active Turkers, we report quality scores as the average per-turker quality, where a Turker's quality is just the average quality of all the assignments that the Turker completed.

\textbf{Or in otherwords, because $\sum$ in latex is so lovely:}
\begin{align}	
	Quality(turker_i) = \frac{\sum_{a_j \in Assigns(i)}Quality(a_j)}{\mid Assigns(i) \mid}
\end{align}	
where $Assigns(i)$ is the assignments completed by turker $i$, and $Quality(a)$ is as above.
